2H qSIP Calculations

### 2021-09-06 qSIP_calculations.Rmd
gencalc fixed to use at%

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel)
```

@@

peaks_mapped <- peaks_mapped %>% 
  group_by(sample_id) %>% 
  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
         f_label = 0.005)

@@

peaks_mapped_active <- peaks_mapped %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

```{r}
gen_calc_data <- peaks_mapped_active %>% 
  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, terrain, f_start)) %>% 
  mutate(at2H_label = 0.005) %>% 
  mutate(f_label = 0.005, # label is 0.5 at%
         a = 0.5,
         #R = (d2H/1000 +1) * ref_ratio,
         t = inc_time_d,
         #f_t = R / (1 + R) %>%  # 2F at time t where t = inc_time_d
         f_t = at2H) %>% 
  group_by(compound) %>% 
  mutate(
    t0 = 0,
    d_ft = as.numeric(f_t - f_start), # change in isotopic enrichment from start to time t
    d_t = t - t0, # change in time from start to time t (days)
    u_d = gencalc(a = a, FT = f_t, F0 = f_start, FL = f_label, t = d_t) # turnover (µ) in days^-1
  )

gen_calc_data
```

@@

```{r "shaded chromatogram", fig.width=8, fig.height=8}
peaks_mapped_active %>% ggplot(
  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
  geom_col(aes(width = rt_end - rt_start)) +
  scale_fill_viridis_c() +
  facet_wrap(~sample_id, ncol = 1) +
  geom_label_repel(size = 2, box.padding = 1) +
  coord_cartesian(ylim = c(0, 1300)) +
  labs(fill = "2F",
         x = "Retention Time (s)",
         y = "Amplitude (mV)")
```

>>>>

```{r, message=FALSE, warning=FALSE}
library(tidyverse) # general data wrangling and plotting
library(isoreader) # reading the raw data files
library(isoprocessor) # processing the data
library(isotopia) # isotope utilities
library(readxl) # reading excel docs
library(ggsci) # some nice color palettes
library(ggborderline) # nice looking ggplot lines
library(ggrepel)
library(latex2exp)
library(ggdist)
```

@@

peaks_mapped <- peaks_mapped %>% 
  group_by(sample_id) %>% 
  mutate(inc_time_d = as.numeric(substr(sample_id, 4,4)),
         inc_time_d_str = paste(inc_time_d, "Days"),
         f_label = 0.005)

@@

```

## Remove standards from gencalcs
```{r}
peaks_mapped_active <- peaks_mapped %>% 
  filter(str_detect(compound, "STD", negate = TRUE))
```

```{r}
gen_calc_data <- peaks_mapped_active %>% 
  select(c(Analysis, compound, d2H, at2H, sample_id, inc_time_d, inc_time_d_str, terrain, f_start)) %>% 
  mutate(
    at2H_label = 0.005,
    f_label = 0.5, # label is 0.5 at%
    a = 0.5, # assimilation efficiency
    t0 = 0, # start time
    d_t = inc_time_d - t0, # change in time
    f_t = at2H, # restate 2F at time t
    u_d = gencalc(a = 0.5, # Assimilation efficiency
                  FT = f_t, # 2F at time t (at%)
                  F0 = f_start, # 2F at t0 (at%)
                  FL = f_label, # 2F of label (at%)
                  t = d_t), # change in time
         # Returns turnover (µ) in days^-1
         gen_d = log(2) / u_d # calculate generation time
  )
```

@@

## Chromatogram scaled by 2F
```{r "shaded chromatogram", fig.width=8, fig.height=8}
peaks_mapped_active %>% ggplot(
  aes(x = rt, y = amp2, fill = as.numeric(at2H), label = compound)) +
  geom_col(aes(width = rt_end - rt_start)) +
  scale_fill_viridis_c(option = "magma") +
  facet_wrap(~inc_time_d_str, ncol = 1) +
  geom_text_repel(size = 2, box.padding = 0.5, nudge_y = 150) +
  theme_classic() +
  coord_cartesian(ylim = c(0, 1300)) +
  labs(fill = TeX("$^2F$"),
         x = "Retention Time (s)",
         y = "Amplitude (mV)") +
  theme(strip.background = element_blank())
```

```{r}
gen_calc_data %>% filter(inc_time_d != 0) %>% 
  ggplot(
  aes(x = gen_d, 
      y = inc_time_d_str, 
      color = inc_time_d_str, 
      fill = inc_time_d_str)) +
  stat_slab(height = 0.3) +
  geom_point(
    shape = 124,
    size = 5,
    alpha = 0.5,
    position = position_nudge(y = -.07)) +
  stat_pointinterval(color = "black") +
  scale_x_log10() +
  annotation_logticks(sides = "b") +
  scale_fill_npg() +
  scale_color_npg() +
  theme_classic() +
  labs(x = "Generation time (days)",
       y = "Incubation time") +
  theme(legend.position = "none",
        axis.ticks.y = element_blank())
```
